---
title: "Mark Druffel"
author: Mark Druffel
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    #resume is the default from pagedown, keep it there or have to build all css structures
    css: ["resume.css", "resume"]
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
    knit: pagedown::chrome_print
---
```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE,
  warning = F,
  message = F
)
library(tidyverse)
library(ragg)
knitr::opts_chunk$set(dev = "ragg_png")
library(showtext)
sysfonts::font_add_google(name = "Roboto Slab", family = "roboto_slab")
showtext::showtext_auto()
```
Aside
================================================================================
<center>
![Mark Druffel](`r paste0(here::here(), "/images/my_photo_tight.jpeg")`){style='width:52%;border-radius: 50%;padding-bottom:8px;'}
<br>
<a href='https://www.mark-druffel.com/' target='_blank'><i class="fa fa-home"></i></a>
<a href='mailto:mark.druffel@gmail.com' target='_blank'><i class="fa fa-envelope"></i></a>
<a href='https://github.com/mark-druffel' target='_blank'><i class="fa fa-github"></i></a>
<a href='https://www.linkedin.com/in/markdruffel/' target='_blank'><i class="fa fa-linkedin"></i></a>
<a href='https:/stackoverflow.com/users/6213809/mark-druffel' target='_blank'><i class="fa fa-stack-overflow"></i></a>
</center>

<i class="fa fa-graduation-cap" style='padding-right:6px;'></i> Education {#education}
--------------------------------------------------------------------------------
#### University of Notre Dame
M.S in Business Analytics  

#### Ohio University 
Bachelors in Business Admin

<i class="fa fa-terminal" style='padding-right:6px;'></i> Languages {#languages}
--------------------------------------------------------------------------------
```{r, out.width="90%"}
skills_bar <- function(){
  tibble(
    order = c(1, 2, 3, 4 ,5 , 6, 7),
    language = c("R", "Python", "SQL", "Cypher", "JavaScript", "HTML/CSS", "Bash"),
    skill = c(5, 3.5, 5, 2, 3, 3.5, 3)
  ) |>
    mutate(max = 5) |>
    ggplot(aes(x = max, y = reorder(language, -order), width = .6)) +
    geom_col(fill = "grey85") +
    geom_col(aes(x = skill), fill = "grey15") +
    theme_void() +
    labs(y = "Language") +
    theme(
      axis.text.y = element_text(size = 52, family = "roboto_slab", face = "bold", color = "black", hjust = 1),
      plot.background = element_rect(fill = "#F5FEFD", color = "#F5FEFD"),
      panel.background = element_rect(fill = "#F5FEFD", color = "#F5FEFD")
    )
}
skills_bar()
```

<i class="fa fa-wrench" style='padding-right:6px;'></i> Tools {#tools}
--------------------------------------------------------------------------------
#### Database / Big Data
Snowflake, Aurora, SQL, Spark, Databricks, Apache Arrow, neo4j, dbplyr, data.table

#### Data Visualization / Dashboard  
ggplot2, plotnine, shiny, observable, d3.js, Plotly, Highcharts, Apache Superset, Tableau, PowerBI

#### Modeling
tidymodels, caret, keras, tidytext, Apache OpenNLP

#### Devops  
Git, Github, AWS, Azure, Digital Ocean, Docker, Apache Airflow, Kedro, targets, Quarto, nbdev, Netlify

#### Design
InVision, Figma, Gimp, Scribis


<i class="fa fa-sitemap" style='padding-right:6px;'></i> Volunteer {#organizations}
--------------------------------------------------------------------------------
#### Civic Software Fdn, Exec Producer  
Delivered a web app that provided longitudinal analysis to the Oregon Department of Education.

Main
================================================================================

Mark Druffel <span class="my-location"><i class="fa fa-map-marker-alt" style='padding-right:4px;'></i>Portland, OR</span> {#title}    
--------------------------------------------------------------------------------
<span class="my-blurb">Data scientist with a decade of experience. I love to problem solve, build things, and use data visualization tell stories and build rich experiences. 

Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Lead Data Scientist

84.51°

Remote

2022

Enable Kroger's personalization and loyalty team to design and execute random controlled trials (RCT) to measure the success of targeted marketing campaigns.  

* Design campaign measurement dashboards and reports for marketing teams
* Led the team's data pipeline refactor project which improved velocity, code quality, and enabled new capabilities

### Senior Data Analyst

DocStation

Remote

2021

Founding member and first analytics hire for a seed funded start-up.  

* Expanded the data warehouse by developing data models in the pipeline with SQL, pyspark, and Airflow  
* Designed and developed dashboards that were used by business operations using Apache Superset and R Shiny  
* Led analysis projects that improved task targeting, sales, and user retention   

### Data & Analytics Consultant

Propeller

Portland, OR

2017

Worked with clients to develop strategies and road maps and execute projects.

* Created a feedback loop between a product team and their end-users by developing a text analysis and NLP pipeline, which automatically identified user pain points 
* Designed a prototype app that enabled an HR team to transition to a data-driven recruitment process, improving velocity and candidate quality 
* Developed and facilitated an analytics workshops
* Developed internal analytics infrastructure to streamline Propeller's operations including API wrappers, a data pipeline, and automated reporting  

### Business Intelligence Manager

Northern Trust, Hedge Fund Services

Chicago, IL

2013

Managed a global team that directly served business partners and end users.   

* Designed and developed an analytics pipeline that identified bottlenecks, forecasted server demand, etc. to measure and manage tech debt
* Developed dashboards and reporting using Tableau and eGlue (homegrown)
* Managed tech services on behalf of the business including access management, data transfer, and data quality assurance
* Trained my team in Excel, SQL, Tableau, R, and Python 
        
### Senior Consultant

Plante Moran

Chicago, IL

2011

Managed IT audits and risk assessments for clients in various industries

### Staff Auditor 

Fifth Third Bank

Cincinnati, OH

2010

Executed financial audits, IT audits, and risk assessments 


<footer> 
<p class="footer">Resume made with `r fontawesome::fa("r-project", fill = "steelblue")` & [pagedown](https://github.com/rstudio/pagedown), code available on `r fontawesome::fa("github", fill = "black")` [GitHub](https://github.com/mark-druffel/resume)<br/>[mark.druffel@gmail.com](mailto:mark.druffel@gmail.com)
<p/>
</footer>
